Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-13 ms/SI.Rmd
typo

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
CV: coefficient variance

@@

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter.

>>>>

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
CV: coefficient of variation

@@

Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
Species was used as a random intercept.
The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
